Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-06 paper.tex
edits

In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,gv}^{-1}$.
We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
% such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. 
The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Li1990, Gong2015}
This means that it is difficult to isolate $B$ terms when $A$ terms are present.
As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.

>>>>

In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,gv}^{-1}$.
We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
This means that it is difficult to isolate $B$ terms when $A$ terms are present.
As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.

### 2024-09-06 si.tex
edits

It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^b$, $b \in \mathbf{N}$. 
Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
\begin{equation}\label{integral}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta)
\end{equation}
When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \exp(-q^2 - q\Delta) &= \int \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int \mathrm{d}q \exp(-(q + \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}

For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta) = -\partial_{\Delta} \int \mathrm{d}q \ q^{w-1} \exp(-q^2 - q\Delta)
\end{equation}

We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.

Starting with \autoref{key},
\begin{equation}
\begin{split}
	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
\end{split}
\end{equation}
Using the fact that $H_0(q) = 1$ and $H_1(q) = 2q$, 
\begin{equation}\label{HT10}
	\begin{split}
		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
	\end{split}
\end{equation}
These integrals are now easily evaluated using \autoref{identity}:
\begin{subequations}\label{evalGaussians}
	\begin{equation}
		\begin{split}
					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
					& = -\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)
		\end{split}
	\end{equation}
giving
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
	\end{split}
\end{equation}
\end{subequations}
With $\tilde{N} = N(1)*N(0) = (1! \ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0! \ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
\begin{equation}
	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
\end{equation}
The evaluation of other Herzberg-Teller integrals follows a similar process.
These results have been tabulated by Carlson. \cite{Carlson1988thesis}

\section{Impact of $\Delta$ on $A,B$ Terms in HDFG Spectra}
In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.

>>>>

It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^w$, $w \in \mathbf{N}$. 
Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
\begin{equation}\label{integral}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta)
\end{equation}
When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \exp(-q^2 - q\Delta) &= \int \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int \mathrm{d}q \exp(-(q + \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
 For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta) = -\partial_{\Delta} \int \mathrm{d}q \ q^{w-1} \exp(-q^2 - q\Delta)
\end{equation}

We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.
Starting with \autoref{key},
\begin{equation}
\begin{split}
	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
\end{split}
\end{equation}
Using $H_0(q) = 1$ and $H_1(q) = 2q$,\cite{RN230} 
\begin{equation}\label{HT10}
	\begin{split}
		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
	\end{split}
\end{equation}
These integrals are now easily evaluated using \autoref{identity}:
\begin{subequations}\label{evalGaussians}
	\begin{equation}
		\begin{split}
					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
		\end{split}
	\end{equation}
giving
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
	\end{split}
\end{equation}
\end{subequations}
With $\tilde{N} = N(1)*N(0) = (1! \ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0! \ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
\begin{equation}
	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
\end{equation}
The evaluation of other Herzberg-Teller integrals follows a similar process.
These results have been tabulated by Carlson. \cite{Carlson1988thesis}

\section{Impact of $\Delta$ on $A,B$ Terms in HDFG Spectra}
In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
First, we investigate how the Franck-Condon factors and Herzberg-Teller integrals are manipulated as a function of $\Delta$.
%TODO - plot
